---
title: "Untitled"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problem 1
```{r}
library(lpSolve)
A = matrix(c(-10,5,1,20,10,0),3,2)
A

b = c(22,49,5)
C = c(-1,4)
dir <- c("<=","<=","<=")
b
C

s<-lp("max",C,A,dir,b, all.int = TRUE)
s$status
s$solution
s$objval
```
We can see that this answer matches with the answer we calculated manually

In this case, we have 10 branches with 3 feasible solutions. Thus the difference  = 7

Problem 2
```{r}
library(lpSolve)
A = matrix(c(6,0,1,3,0,1,5,1,0,2,1,0),3,4)
b = c(11,1,1)
C = c(9,5,6,4)
dir <- c("<=","<=",">=")

s<-lp("max",C,A,dir,b, all.bin = TRUE)
s$status
s$solution
s$objval
```

Thus, building a factory in Austin and a factory and warehouse in Dallas will be the optimal strategy

Problem 3
```{r}
library(lpSolve)
A = matrix(0,12,12)
b = c(rep(1,12))
C = c(rep(1,12))
dir <- c(rep("<=",12))

A[1,3]=1
A[1,5]=1
A[1,7]=1
A[1,8]=1
A[1,9]=1
A[2,8]=1
A[2,9]=1
A[3,1]=1
A[3,7]=1
A[3,8]=1
A[3,9]=1
A[4,10]=1
A[5,1]=1
A[5,7]=1
A[6,10]=1
A[6,11]=1
A[7,1]=1
A[7,3]=1
A[7,5]=1
A[8,1]=1
A[8,2]=1
A[8,3]=1
A[8,9]=1
A[9,1]=1
A[9,2]=1
A[9,3]=1
A[9,8]=1
A[10,4]=1
A[10,6]=1
A[10,11]=1
A[10,12]=1
A[11,6]=1
A[11,10]=1
A[11,12]=1
A[12,10]=1
A[12,11]=1

s<-lp("max",C,A,dir,b, all.bin = TRUE)
s$status
s$solution
s$objval
```

Problem 4
```{r}
library(lpSolve)
A = matrix(c(1,1,1,4,0,0,0,3,0,0,0,2,3,1,0,2,0,1,1,2,0),3,7)
b = c(233,148,106)
C = c(rep(1,7))
dir <- c(">=",">=",">=")

s<-lp("min",C,A,dir,b, all.int = TRUE)
s$status
s$solution
s$objval
```

Thus the solution is :
105 rolls using (25,37,54)
2 rolls using (25,25,25,25)
1 roll using (37,37,37)
1 roll using (54,54)
40 rolls using (25,25,25,37)

to give minimum number of rolls used = 149

```{r}
library(lpSolve)
A = matrix(c(0),7,7)
b = c(5,13,12,10,14,8,6)
C = c(rep(1,7))
dir <- c(rep(">=",7))
A[1:5,1] = 1
A[2:6,2]=1
A[3:7,3]=1
A[1,4]=1
A[4:7,4]=1
A[1:2,5]=1
A[5:7,5]=1
A[1:3,6]=1
A[6:7,6]=1
A[1:4,7]=1
A[7,7]=1

s<-lp("min",C,A,dir,b, all.int = TRUE)
s$status
s$solution
s$objval
```

Thus, the solution is : 
1 worker who takes leave on Monday Tuesday
8 workers who take leave on Tuesday Wednesday
2 workers who take leave on Wednesday Thursday
0 workers who take leave on Thursday Friday
3 workers who take leave on Friday Saturday
1 worker who takes leave on Saturday Sunday
0 workers who take leave on Sunday Monday

